\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Kyra Dunning}\\ 
    \hrulefill
\end{center}

\begin{center}
    8 Missenden Rd \textbullet \ Camperdown, 2050 \textbullet \ kyra.dunning@outlook.com \textbullet \ (61+) 0481194070 \textbullet \ \href{https://www.linkedin.com/in/kyra-dunning/}{LinkedIn}
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}\\
    \hrulefill
\end{center}
\textbf{University of Sydney} \hfill Sydney, NSW

B. Advanced Computing and B. Science,  
Computer Science and Geology \& Geophysics.
\hfill February 2023 – November 2027

\vspace{12pt}

%EXPERIENCE

\begin{center}
    \textbf{Experience}\\ 
    \hrulefill
\end{center}

\textbf{Code Camp} \hfill Sydney, NSW

\textbf{Teaching Instructor and Assistant} \hfill May 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Deliver Code Camp programs to a class of up to 25 students.
    \item Support the class Head Teacher to provide one on one help to individual students during class and keep students on track.
    \item Working with kids in a team environment.
\end{itemize}

\vspace{12pt}

\textbf{University of Sydney} \hfill Sydney, NSW

\textbf{Extended Bachelor Program (EBP) Mentor} \hfill May 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item I support fellow Indigenous peers with their studies at the University of Sydney who are currently undertaking the Extended Bachelor Program.
    \item This support includes dedicating time each week to sit with them and provide general guidance on various activities they need to undertake, such as checking what's due for each of their units, reading over assignments with them, helping them with the process of submitting assignments on Canvas, and providing an extra supportive push to get work done. 
    \item It's important to note that this is not an 'academic' role in the traditional sense, but rather an academic support role where I assist students with their studies without actively teaching them content.
\end{itemize}

\textbf{Student Ambassador} \hfill March 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Represent the University across a range of recruitment events such as Open Day, campus tours, career markets, in-school visits, residential programs and online webinars.
    \item Share my lived experience as a university student to demystify concepts of higher education.
    \item Learn and maintain a solid understanding of university degrees, programs, pathways and admission criteria.
    \item Facilitate discussions with high school students about my aspirations, how to achieve them and increase their knowledge about degree options.
\end{itemize}

\vspace{12pt}

\textbf{Macquarie Group} \hfill Sydney, NSW

\textbf{Cybersecurity Intern} \hfill December 2023 – February 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked among the Cyber Metronome team within Cybersecurity Governance in the Corporate Operations Group at Macquarie Group.
    \item Gained knowledge, exposure and experience in gathering user requirements, understanding those requirements and creating draft user stories to improve these products for asset owners and managing teams alike.
    \item Worked alongside a range of tech professionals to learn about and assist in providing products that asset/service owners across Macquarie can use to determine if they are meeting cybersecurity expectations, while also providing a path to remediate/implement said expectations if required.
    \item Gained experience in Jira and Confluence (Atlassian).
\end{itemize}

\vspace{12pt}

\textbf{John Holland Group} \hfill Rhodes, NSW

\textbf{IT Undergraduate} \hfill August 2023 – November 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Delved into the intricacies of the M7-M12 project, gaining hands-on experience in addressing the challenges inherent in managing IT systems across multiple worksites. 
    \item Provided hybrid desktop support for staff, offered technical assistance both on-site and remotely, gained knowledge in how to configure Wi-Fi networks, and facilitated staff on-boarding processes, among other tasks. 
    \item Familiarized myself with a range of software and platforms crucial to project management, including computer systems, hardware configurations, ServiceNow, task management tools, and database systems. 
\end{itemize}

\vspace{12pt}

\textbf{University of Sydney, Fisher Library} \hfill Sydney, NSW

\textbf{Access Services Assistant} \hfill May 2023 – November 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Duties included a range of digitisation tasks, quality checking and control, and compilation of media. 
    \item Digitised various media, such as 35mm film slides and hard
cover books.
    \item Provided feedback on the usability of the new developing Library site.
    \item Worked on the A-Z Rare Books Exhibition.
\end{itemize}

%VOLUNTEERING

\begin{center}
    \textbf{Volunteering}\\ 
    \hrulefill
\end{center}

\textbf{Sydney Computing Society - SYNCS} \hfill Sydney, NSW

\textbf{Systems Administration Subcommittee} \hfill March 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Maintain SYNCS front-end and back-end products.
    \item Update SYNCS website to display current information.
    \item Work with others using GitHub, Git/Bash, JavaScript, HTML and Python.
    \item Create and maintain SYNCS tech event infrastructures.
\end{itemize}

\vspace{12pt}

\textbf{The Matilda Centre for Research in Mental Health and Substance Use} \hfill Sydney, NSW

\textbf{Youth Advisory Board Member} \hfill March 2023 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked alongside the other young people to co-design a range of resources aiming to support researchers and mental health professionals on how best to engage young people in mental health and substance use research.
    \item Actively participated being on Judging Panel for Matilda Centre Awards 2023.\\
    \textit{Involved in}:
    \item Youth Priorities Project
    \item Australian Government's Measuring What Matters Statement.
    \item Aboriginal Health Impact Statement: NSW Strategy for Young People's Health and Wellbeing 2025+.
    \item Associate Investigator on MRFF Grant / Optimising efficiency through tailored solutions: Co-design and trial of an adaptive, scalable web-based intervention to reduce alcohol use and related harms in youth.
    \item Youth Health and Wellbeing Framework 2025+ Consultation Plan.
\end{itemize}

\vspace{12pt}

\textbf{Consumer and Community Involvement Program} \hfill Sydney, NSW

\textbf{Health Consumers and AI Consumer Reference Group Member} \hfill April 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item I support the development of a resource for consumers about AI in healthcare, as well as participate in conversations about uses of AI in health systems and services. The resulting plain-language document will be made freely available.
\end{itemize}

\vspace{12pt}

\textbf{University of Sydney - Gadigal Centre} \hfill Camperdown, NSW

\textbf{MOBS Mentor} \hfill March 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Foster meaningful connections, exchange knowledge and experiences, and embark on a journey of mutual learning and development to contribute to the success of my fellow participants. 
\end{itemize}

\vspace{12pt}

\textbf{Sancta Sophia College} \hfill Camperdown, NSW

\textbf{Student Ambassador} \hfill January 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item I help give tours to senior high school students interested in attending university, as well as incoming students at Sancta Sophia College on multiple occasions.
\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Awards \& Activities}\\
    \hrulefill
\end{center}

\textbf{Jane Street} \hfill Hong Kong, China

\textbf{Wise undergrad Participant} \hfill January 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Attended as one of forty first-year female STEM undergrad students invited.
    \item Learnt about the challenging ways they use concepts relating to mathematics, computer science and probability in trading.
    \item Made some lifelong connections with others studying STEM degrees from around the world.
    \item Networked with Jane Street’s traders and technologists, who shared the extensive, transitioning path from their STEM degree to their current role, and the relevant skills they have learnt along the way.
    \item Attending this program developed important interpersonal, team-building and leadership skills.
    \item Extended knowledge of financial markets, and the ways mathematics, programming, research and data science relate to roles in trading.
\end{itemize}

\vspace{12pt}

\textbf{John Holland Group \& NSW AECG} \hfill Sydney, NSW

\textbf{Aboriginal and Torres Strait Islander STEM Scholarship by NSW AECG and John Holland Group} \hfill May 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Awarded this scholarship in 2023 and offered casual, ongoing paid work experience at a John Holland Group (JHG) project or corporate office while completing university studies.
\end{itemize}

\vspace{12pt}

\textbf{University of Sydney} \hfill Sydney, NSW

\textbf{CAE Aboriginal and Torres Strait Islander Engineering Scholarship} \hfill March 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Awarded this scholarship in 2023 to support my studies in engineering at the Faculty of Engineering, University of Sydney.
\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Skills}\\
    \hrulefill
\end{center}

\textbf{Technical:} Python, Java, R, C, C++, Git, Bash, Object-Oriented Programming, Visual Studio Code, Confluence, Jira, Scrum, Amazon Web Services, Ubuntu.

\textbf{Language:} English (fluent), Japanese (beginners).



\end{document}